---
title: "CLT_WUP"
author: "Jaylen Johnson"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

kkardashtemp  see code below

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(lattice)
```

```{r}
Homers_data <- read.csv(file="Homers_data.csv")

my1000 <- sample(Homers_data , size = 1000, replace=T)

```

```{r}

library(ggplot2)
sampleNumber = sample(1:10000, size = 1000)
library(dplyr)
my1000 <- Homers_data[sampleNumber, ]
names(my1000)
# Basic density
p <- ggplot(my1000, aes(x=kkardashtemp,col=sex)) + 
  geom_density()
p
# Add mean line
p+ geom_vline(aes(xintercept=mean(kkardashtemp)),
            color="blue", linetype="dashed", size=1)
print(paste('mean = ', mean(my1000$kkardashtemp),' sd = ',sd(my1000$kkardashtemp)))
```

```{r}
numb=2
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k2 = x.avg

p <- ggplot(my1000, aes(x=k2)) + 
  geom_density() 
p

# Add mean line
  geom_vline(aes(xintercept=mean(k2)),
            color="blue", linetype="dashed", size=1)
print(paste('mean = ', mean(my1000$k2),' sd = ',sd(my1000$k2)))

```
## We expect the sample mean to be close to population and the standev to get smaller by the ratio of one to the sample size. In this case 1/sqrt(2)

### There are 3 peaks in the density plot. You pick two people you can get MM,MF.FM,or FF. these are all equally likey so the little peak on left is all the FF's while the little peak on the right is all the MM's so the big one in the middle is both the MF and FM in the same bag so-to-speak.  

```{r}
numb = 4
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k4 = x.avg


p <- ggplot(my1000, aes(x=k4),col=sex) + 
  geom_density() +

# Add mean line
 geom_vline(aes(xintercept=mean(k4)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 4") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k4),' sd = ',sd(my1000$k4)))

```




```{r}
numb = 9
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k9 = x.avg


p <- ggplot(my1000, aes(x=k9),col=sex) + 
  geom_density() +

# Add mean line
 geom_vline(aes(xintercept=mean(k9)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 9") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k9),' sd = ',sd(my1000$k9)))

```
This graph is appearing unimodal around where we have 9 samples. However we have a bimodal distribution in the beginning and end of the graphs where they progress towards a unimodal distribution. 

```{r}
numb = 16
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k16 = x.avg


p <- ggplot(my1000, aes(x=k16),col=sex) + 
  geom_density() +

# Add mean line
 geom_vline(aes(xintercept=mean(k16)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 16") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k16),' sd = ',sd(my1000$k16)))

```

The 16 sample graph looks more unimodal than the 9 graph.

```{r}
numb = 25
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k25 = x.avg


p <- ggplot(my1000, aes(x=k25),col=sex) + 
  geom_density() +

# Add mean line
 geom_vline(aes(xintercept=mean(k9)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 25") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k25),' sd = ',sd(my1000$k25)))

```


With 25 samples the graphs are becoming more unimodal compared to the previous lesser sampled graphs.

```{r}
numb = 36
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k36 = x.avg


p <- ggplot(my1000, aes(x=k36),col=sex) + 
  geom_density() +

# Add mean line
 geom_vline(aes(xintercept=mean(k9)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 36") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k36),' sd = ',sd(my1000$k36)))

```

These samples show Central Limit Theorem.  While increasing the sample sizes we begin to get graphs that look more unimodal then the ones preivous.  This sample size of 36 provided a graph that is more unimodal than the ones previous




